\textit{Supplemental materials for:} High-order cognition is supported by information-rich but compressible brain activity patterns

### 2023-03-16 paper/supplement.tex
finished complete drafts of main text and supplement

\caption{\textbf{Top terms associated with the highest-weighted components by
condition, broken down by story segment.} Each group of five rows corresponds
to an experimental condition (denoted by color, as indicated in the legend in
the lower right), and the columns and shading correspond to the component
number (ranked by proportion of variance explained). The colored squares in
front of many of the topics denote manually identified cognitive labels
(Tab.~\ref{tab:topics}).}

@@

\caption{\textbf{Brain maps by component and condition.} For the top five
highest-weighted principal components (rows), from each experimental condition
(columns), the components' brain maps are projected onto four views: left
sagittal, axial, right sagittal, and coronal.  The color scale is the same for all panels and matches the coloring in Fig.~\neurosynth C.}

@@

\caption{\textbf{Functions associated with top-weighted components by
condition.} \textbf{A. Top-weighted topics by condition.} Here we display
per-condition (rows, indicated by colored dots) topic correlations, averaged
across topics that pertain to each of several broad cognitive functions
(columns within each sub-panel, indicated by colored dots). Each sub-panel
reflects correlations for the components indicated in the panel titles. A
legend for the condition and cognitive function classifications is displayed in
the lower right of the figure. Table~\ref{tab:topics} provides a list of each topic's
top-weighted terms, along with each topic's manually labeled cognitive
classification. A full list of the topics most highly associated with each
component may be found in Figure~\ref{fig:top-terms}. \textbf{B. Associations
between per-condition components and cognitive functions.} The network plots
denote positive average correlations between the component images for each
condition (gray-outlined dots on the left sides of each network; colors denote
conditions) and topic-specific brain maps associated with each indicated
cognitive function (black-outlined dots on the right sides of each network;
colors denote cognitive functions). The line thicknesses are proportional to
the correlation values (correlation coefficients are noted in the heatmaps in
Panel A). \textbf{C. Correlations between each principal component, by
condition.} The heatmaps display the correlations between the brain maps
(Fig.~\ref{fig:components}) for each principal component (sub-panel), across each
pair of conditions (rows and columns of each sub-panel's matrix, indicated by
colored dots). \textbf{D. Associations between per-condition topic weights, by
component.} Each sub-panels network plot summarizes the pattern of correlations
between the topic correlations from each of the $n$\textsuperscript{th}
top-weighted principal components (sub-panel), for each experimental condition
(gray-outlined dots). The line thicknesses are proportional to the correlation
values (correlation coefficients are noted in the heatmaps in Panel C).}

>>>>

\caption{\textbf{Highest-weighted topics associated with the highest-weighted
components by condition, broken down by story segment.} Each group of five rows
corresponds to an experimental condition (denoted by color, as indicated in the
legend in the lower right), and the columns and shading correspond to the
component number (ranked by proportion of variance explained). The colored
squares in front of many of the topics denote manually identified cognitive
labels (Tab.~\ref{tab:topics}).}

@@

\caption{\textbf{Brain maps by component and condition.} For the top five
highest-weighted principal components (rows), from each experimental condition
(columns), the components' brain maps are projected onto four views: left
sagittal, axial, right sagittal, and coronal. The color scale is the same for
all panels and matches the coloring in Figure~\neurosynth C.}

@@

\caption{\textbf{Functions associated with top-weighted components by
condition.} \textbf{A. Top-weighted topics by condition.} Here we display
per-condition (rows, indicated by colored dots) topic correlations, averaged
across topics that pertain to each of several broad cognitive functions
(columns within each sub-panel, indicated by colored dots). Each sub-panel
reflects correlations for the components indicated in the panel titles. A
legend for the condition and cognitive function classifications is displayed in
the lower right of the figure. Table~\ref{tab:topics} provides a list of each topic's
top-weighted terms, along with each topic's manually labeled cognitive
classification. A full list of the topics most highly associated with each
component may be found in Figure~\ref{fig:top-terms}. \textbf{B. Associations
between per-condition components and cognitive functions.} The network plots
denote positive average correlations between the component images for each
condition (gray-outlined dots on the left sides of each network; colors denote
conditions) and topic-specific brain maps associated with each indicated
cognitive function (black-outlined dots on the right sides of each network;
colors denote cognitive functions). The line thicknesses are proportional to
the correlation values (correlation coefficients are noted in the heatmaps in
Panel A). \textbf{C. Correlations between each principal component, by
condition.} The heatmaps display the correlations between the brain maps
(Fig.~\ref{fig:components}) for each principal component (sub-panel), across each
pair of conditions (rows and columns of each sub-panel's matrix, indicated by
colored dots). \textbf{D. Associations between per-condition topic weights, by
component.} Each sub-panel's network plot summarizes the pattern of correlations
between the topic correlations from each of the $n$\textsuperscript{th}
top-weighted principal components (sub-panel), for each experimental condition
(gray-outlined dots). The line thicknesses are proportional to the correlation
values (correlation coefficients are noted in the heatmaps in Panel C).}
